Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-04 paper.tex
shorten conclusion

We also observe that transparent hugepages can induce significantly earlier
    onset of memory pressure in workloads that have random access patterns,
    which may nullify the benefits from better TLB behavior. This can happen
    even in workloads that would not otherwise experience memory pressure.

Finally, we observe that the 99.99-th percentile of disk latency during swapping
    can account for over 70\% of runtime for the workloads we tested.

>>>>

In addition, transparent hugepages can induce significantly earlier
    onset of memory pressure in workloads that have random access patterns,
    which may nullify the benefits from better TLB behavior. This can happen
    even in workloads that would not otherwise experience memory pressure.
Finally, we see that the 99.99-th percentile of disk latency during swapping
    can account for over 70\% of runtime for the workloads we tested.
